---
title: "Original Study: Data Visualization"
author: "Group 10"
output: 
  html_document:
    toc: true
    toc_depth: 2
    highlight: tango
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, error = F, message = F, warning = F)

```

```{r libraries, include=FALSE, message=FALSE, warning=FALSE}

# package for convenience functions (e.g. ggplot2, dplyr, etc.)
library(tidyverse)

# package for visualization
library(tidybayes)

# package to visualize 
library(bayesplot)

# package to extract HDIs
library(HDInterval)

#devtools::install_github("michael-franke/aida-package")
library(aida)

# use the aida-theme for plotting
theme_set(theme_aida())

# global color scheme / non-optimized
project_colors = c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#000000")

# setting theme colors globally
scale_colour_discrete <- function(...) {
  scale_colour_manual(..., values = project_colors)
}
scale_fill_discrete <- function(...) {
   scale_fill_manual(..., values = project_colors)
} 

# define scale function to avoid matrix object in tibble
my_scale <- function(x) c(scale(x))

```

```{r}
#loading for analysis prepared data table
animal <- read.csv('~/CS-SS20/Experimental_Psychology_Lab/Final_Project/XPLab2020_FinalProject/pilot/Original_Study/animal_data_cleaning/animal_data.csv')

animal
```

##Data Analysis - Original Study 

For the main trials of our experiment we hold the following research hypotheses:

H1: The area under the curve (AUC) is larger for atypical trials compared to typical trials.

H2: The maximal absolute deviation (MAD) is larger for atypical trials compared to typical trials.

H3:Movement duration is longer for atypical trials compared to typical trials.

H4:The likelihood of obtaining different cluster types depends on the experimental conditions.

H5:The total categorisation response time is longer for atypical trials compared to typical trials.

H6:The movement initiation latency is longer for atypical trials compared to typical trials.

H7:The distance travelled in pixels is  longer for atypical trials compared to typical trials.


##Data Vizualisation 
H1: The area under the curve (AUC) is larger for atypical trials compared to typical trials.
```{r}
#Taking absolute AUC values, since negative AUC make no sense
animal$AUC_abs = abs(animal$AUC)

#We take the median, because it is less influenced by outliers 
median_AUC <- animal %>% 
  group_by(trial_type) %>% 
  dplyr::summarize(AUC_median = median(AUC_abs, na.rm = TRUE)) 
median_AUC

#Plotting AUC_abs for each trial_type
ggplot(animal,
       aes(x = trial_type,
           y = AUC_abs,
           color = trial_type, fill = trial_type))+
  geom_point(alpha = 0.5, size = 3)+
  geom_point(data = median_AUC, aes(x= trial_type, y = AUC_median), color = "black", alpha = 1.0, size = 8, shape = 21)+
  geom_point(data = median_AUC, aes(x= trial_type, y = AUC_median, color = trial_type), alpha = 1.0, size = 7)+
  scale_y_continuous(limits = c(0,350000))+
   ggtitle("Fig. 1: Absolute AUC for each trial type")

```

Fig. 1: The point plot shows the ablsoute Area under the Curve (AUC_abs) values for the respective trial type. The smaller points represent the AUC_abs values for every trial and the big points show the medians of AUC_abs for each trial type. The median AUC_abs values for the Atypical trial type is only slightly higher than for the Typical trial type, wherefore this difference might not be noteworthy.   

H2: The maximal absolute deviation (MAD) is larger for atypical trials compared to typical trials.
```{r}
#Taking absolute MAD values, since negative MAD make no sense
animal$MAD_abs = abs(animal$MAD)

#We take the median, because it is less influenced by outliers 
median_MAD <- animal %>% 
  group_by(trial_type) %>% 
  dplyr::summarize(MAD_median = median(MAD_abs, na.rm = TRUE)) 
median_MAD

#Plotting MAD_abs for each trial_type
ggplot(animal,
       aes(x = trial_type,
           y = MAD_abs,
           color = trial_type, fill = trial_type))+
  geom_point(alpha = 0.5, size = 3)+
  geom_point(data = median_MAD, aes(x= trial_type, y = MAD_median), color = "black", alpha = 1.0, size = 8, shape = 21)+
  geom_point(data = median_MAD, aes(x= trial_type, y = MAD_median, color = trial_type), alpha = 1.0, size = 7)+
  scale_y_continuous(limits = c(0,1000))+
   ggtitle("Fig. 2: Absolute MAD for each Trial Type")

```

Fig. 2: The point plot shows the ablsoute Maximum Absolute Deviation (MAD_abs) values for the respective trial type. The smaller points represent the MAD_abs values for every trial and the big points show the medians of MAD_abs for each trial type. The median MAD_abs values for the Atypical trial type is only slightly higher than for the Typical trial type, wherefore this difference might not be noteworthy.

H3:Movement duration is longer for atypical trials compared to typical trials.
```{r}
#log-tranforming mousetracking duration values for better handling -> there are no negative mousetracking durations 
animal$mousetrackingDuration_log <- log(animal$mousetrackingDuration)

#We take the median, because it is less influenced by outliers
median_move_dur <- animal %>% 
  group_by(trial_type) %>% 
  dplyr::summarize(move_dur_median = median(mousetrackingDuration_log, na.rm = TRUE)) 
median_move_dur

#Plotting Mousetracking Duration for each trial type
ggplot(data = animal,
       aes(x = mousetrackingDuration_log,
           color = trial_type, fill = trial_type))+
  geom_density(alpha = 0.3)+
  #Adding mean RT values as a dashed line 
  geom_vline(data= median_move_dur, aes(xintercept= move_dur_median, color= trial_type), linetype = "dashed", size = 2)+
  scale_fill_manual(values = c("orange", "blue"))+
  scale_color_manual(values = c("orange", "blue"))+
  scale_x_continuous(limits = c(5,10))+
   ggtitle("Fig. 3: Mousetracking Duration for each Trial Type")

```

Fig. 3: The graph shows a density plot of the data displaying the median log-transformed mousetracking duration (move_dur_median) for each trial type (dashed lines) and the distribution of log transformed mousetracking duration for each trial type of each trial (colored density distribution for respective trial type). The log transformed mousetracking duration values for each trial type are differently distributed. For the Typical trial type there is a high peak between [7,8] and the distribution is more narrow than for the Atypical trial type. The peak for the Atypical trial type is also around [7,8] but remarkably smaller. The distribution of log transformed mousetracking duration values for the Atypical trial type is also much more spread out than for the Typical trial type. The median of log transformed mousetracking duration values for the Atypical trial type is larger than for the Typical trial type. This difference might not be noteworthy.

H4:The likelihood of obtaining different cluster types depends on the experimental conditions.

- Please view plots "Percentage of prototypes" and "Classification of Prototypes for Trial_Type" in file animal_data_cleaning under ##CLUSTER AGGREGATION & PROTOTYPE CLASSIFICATION. 

H5:The total categorisation response time is longer for atypical trials compared to typical trials.
```{r}
#log-tranforming RT values for better handling -> there are no negative RT 
animal$RT_log <- log(animal$RT)

#We take the median, because it is less influenced by outliers
median_RT <- animal %>% 
  group_by(trial_type) %>% 
  dplyr::summarize(RT_median = median(RT_log, na.rm = TRUE))

#Plotting differnce in RT for respective conditions in desnity plot
ggplot(data = animal,
       aes(x = RT_log,
           color = trial_type, fill = trial_type))+
  geom_density(alpha = 0.3)+
  #Adding mean RT values as a dashed line 
  geom_vline(data= median_RT, aes(xintercept= RT_median, color= trial_type), linetype = "dashed", size = 2)+
  scale_fill_manual(values = c("orange", "blue"))+
  scale_color_manual(values = c("orange", "blue"))+
  scale_x_continuous(limits = c(6,10))+
   ggtitle("Fig. 4: RT for each trial type")

```

Fig. 4: The graph shows a density plot of the data displaying the median log-transformed reaction times (RT_median) for each trial type (dashed lines) and the distribution of RT_log for each trial type of each trial (colored density distribution for respective trial type). The RT_log values for each trial type are differently distributed. For the Typical trial type there is a high peak between [7,8] and the distribution is more narrow than for the Atypical trial type. The peak for the Atypical trial type is also around [7,8] but remarkably smaller. The distribution of RT_log values for the Atypical trial type is also much more spread out than for the Typical trial type. The median of Rt_log values for the Atypical trial type is larger than for the Typical trial type. This difference might not be noteworthy. 


#H6:The movement initiation latency is longer for atypical trials compared to typical trials.
```{r}
#log-tranforming initiation time values for better handling -> there are no negative initiation times
animal$initiation_time_log <- log(animal$initiation_time)


#We take the median, because it is less influenced by outliers
median_ini_latency <- animal %>% 
  group_by(trial_type) %>% 
  dplyr::summarize(ini_latency_median = median(initiation_time_log, na.rm = TRUE))

#Plotting differnce in initiation time for respective conditions in density plot
ggplot(data = animal,
       aes(x = initiation_time_log,
           color = trial_type, fill = trial_type))+
  geom_density(alpha = 0.3)+
  #Adding mean RT values as a dashed line 
  geom_vline(data= median_ini_latency, aes(xintercept= ini_latency_median, color= trial_type), linetype = "dashed", size = 2)+
  scale_fill_manual(values = c("orange", "blue"))+
  scale_color_manual(values = c("orange", "blue"))+
  scale_x_continuous(limits = c(-0,10))+
   ggtitle("Fig. 5: Initiation Time for each trial type")

```

Fig. 5: The graph shows a density plot of the data displaying the median log-transformed initiation time (ini_latency_median) for each trial type (dashed lines) and the distribution of log-transformed initiation times for each trial type of each trial (colored density distribution for respective trial type). The log initiation time values are equally distributed with slight differences. The peak of Atypical values is higher than the peak of Typical values. For the Typical values there is a small peak on the left for small initiation time values. Both distribution display another peak for higher initiation time values. This might indicate a bimodel/multimodal distribution of values (view Bimodality check in animal_data_cleaning!). The medians for both trial types are almost the same. This difference is not noteworthy. 



#H7:The distance travelled in pixels is longer for atypical trials compared to typical trials.
```{r}

#We take the median, because it is less influenced by outliers
median_travel_dis <- animal %>% 
  group_by(trial_type) %>% 
  dplyr::summarize(travel_dis_median = median(traveledDistance, na.rm = TRUE))

#Plotting differnce in traveled distance for respective conditions in density plot
ggplot(data = animal,
       aes(x = traveledDistance,
           color = trial_type, fill = trial_type))+
  geom_density(alpha = 0.3)+
  #Adding mean RT values as a dashed line 
  geom_vline(data= median_travel_dis, aes(xintercept= travel_dis_median, color= trial_type), linetype = "dashed", size = 2)+
  scale_fill_manual(values = c("orange", "blue"))+
  scale_color_manual(values = c("orange", "blue"))+
  scale_x_continuous(limits = c(0,300))+
   ggtitle("Fig. 6: Traveled Distance for each trial type")

```

Fig. 6: The graph shows a density plot of the data displaying the median traveled distance (travel_dis__median) for each trial type (dashed lines) and the distribution of traveled distance for each trial type of each trial (colored density distribution for respective trial type). Both distributions have a high peak between [0,100], whereas the peak for Typical values is remarkably higher than the peak for Atypical values. There is a second and third peak to the right for Atypical values, which might indiate bimodality/multimodality. The median for Atypical values is larger than the median of Typical values. This difference might however not be noteworthy.   


