---
title: "animal_data_analysis"
author: "Christina Popic"
date: "5 August 2020"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, error = F, message = F, warning = F)

```

```{r libraries, include=FALSE, message=FALSE, warning=FALSE}

# package for convenience functions (e.g. ggplot2, dplyr, etc.)
library(tidyverse)

# package for Bayesian regression modeling
library(brms)

# package for visualization
library(tidybayes)

# package to visualize 
library(bayesplot)

# package to extract HDIs
library(HDInterval)

# these options help Stan run faster
options(mc.cores = parallel::detectCores())

#devtools::install_github("michael-franke/aida-package")
library(aida)

# communication with Stan
library(rstan)


# use the aida-theme for plotting
theme_set(theme_aida())

# global color scheme / non-optimized
project_colors = c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#000000")

# setting theme colors globally
scale_colour_discrete <- function(...) {
  scale_colour_manual(..., values = project_colors)
}
scale_fill_discrete <- function(...) {
   scale_fill_manual(..., values = project_colors)
} 

# define scale function to avoid matrix object in tibble
my_scale <- function(x) c(scale(x))

```

```{r}
#loading for analysis prepared data table
animal <- read.csv('~/CS-SS20/Experimental_Psychology_Lab/Final_Project/XPLab2020_FinalProject/pilot/Original_Study/animal_data_cleaning/animal_data.csv')

animal
```

##Data Analysis - Original Study 

For the main trials of our experiment we hold the following research hypotheses:

H1: The area under the curve (AUC) is larger for atypical trials compared to typical trials.

H2: The maximal absolute deviation (MAD) is larger for atypical trials compared to typical trials.

H3:Movement duration is longer for atypical trials compared to typical trials.

H4:The likelihood of obtaining different cluster types depends on the experimental conditions.

H5:The total categorisation response time is longer for atypical trials compared to typical trials.

H6:The movement initiation latency is longer for atypical trials compared to typical trials.

H7:The distance travelled in pixels is longer for atypical trials compared to typical trials.

#REGRESSION MODELS

Hypothesis 1
```{r}
#Taking absolute AUC values, since negative AUC make no sense
animal$AUC_abs = abs(animal$AUC)
animal$AUC_abs_s = my_scale(animal$AUC_abs)

#informative prior
prior_hypo1 <- c(
  #priors for all fixed effects (trial_type)
  set_prior("student_t(3, -2, 10000)", class = "b"),
  #prior for the Intercept
  set_prior("student_t(3, -2, 10000)", class = "Intercept"),
  #prior for all SDs including the varying intercepts and slopes
  set_prior("student_t(3, -2, 10000)", class = "sd")
)

#by-subject_id varying intercepts and varying 
#slope, without slope/intercept correlation
#by-exemplar varying intercept 
model_hypo1 = brm(
  AUC_abs_s ~ trial_type +
    (trial_type || subject_id)+
    (1 |exemplar),
  control=list(adapt_delta=0.99, max_treedepth=15), 
  data = animal,
  prior = prior_hypo1
  )

#looking at model output 
model_hypo1

```

Intercept: 0.31, trial_typeTypical: -0.36. Negative slope of AUC values from Atypical to Typical trial type.

```{r}
#fit the model
pp_check(model_hypo1)

```

```{r}

# Extract the posteriors
posteriors1_trial_type <- model_hypo1 %>%
  spread_draws(b_Intercept, 
               b_trial_typeTypical) %>%
  # calculate posteriors for each individual level
  mutate(Atypical = b_Intercept,
         Typical = b_Intercept + b_trial_typeTypical) %>% 
  select(Atypical, Typical) %>% 
  gather(key = "parameter", value = "posterior") %>% 
  group_by(parameter) %>% 
  summarise(mean_posterior = mean(posterior),
            `95lowerCrI` = HDInterval::hdi(posterior, credMass = 0.90)[1],
            `95higherCrI` = HDInterval::hdi(posterior, credMass = 0.90)[2])
  
posteriors1_trial_type

# Extract the posteriors
posteriors1 <- model_hypo1 %>%
  spread_draws(b_trial_typeTypical) %>%
  select(b_trial_typeTypical) %>% 
  gather(key = "parameter", value = "posterior")  

  
posteriors1


```

```{r}

# plot
ggplot(data = posteriors1_trial_type, 
       aes(x = parameter, y = mean_posterior,
           color = parameter, fill = parameter)) + 
  geom_errorbar(aes(ymin = `95lowerCrI`, ymax = `95higherCrI`),
                width = 0.2, color = "grey") +
  geom_line(aes(group = 1), color = "black") +
  geom_point(size = 4) +
  labs(x = "trial_type",
       y = "posterior AUC scaled")

# plot the regression coefficients
  ggplot(posteriors1, aes(x = posterior, y = parameter)) + 
    # plot density 
    geom_halfeyeh(.width = 0.95) +
    # add axes titles
    xlab("\nAUC") +
    ylab("") +
    # adjust the x-axis 
    scale_x_continuous(limits = c(-10,10)) +
    # add line for the value zero
    geom_segment(x = 0, xend = 0, y = Inf, yend = -Inf,
                 lty = "dashed")
  
  
```

Results: AUC values are higher for Atypical than Typical trial types, due to the negative slope going from the reference level (Atypical) to the Typical trial type. The credible interval of the coefficient trial_typeTypical includes 0, wherefore there is no compelling evidence for the hypothesis to hold true. 

Hypothesis 2
```{r}
#Taking absolute AUC values, since negative AUC make no sense
animal$MAD_abs = abs(animal$MAD)
animal$MAD_abs_s = my_scale(animal$MAD_abs)

#informative prior
prior_hypo2 <- c(
  #priors for all fixed effects (trial_type)
  set_prior("student_t(3, 0, 2.5)", class = "b"),
  #prior for the Intercept
  set_prior("student_t(3, -1, 2.5)", class = "Intercept"),
  #prior for all SDs including the varying intercepts and slopes
  set_prior("student_t(3, 0, 2.5)", class = "sd")
)

#by-subject_id varying intercepts and varying 
#slope, without slope/intercept correlation
#by-exemplar varying intercept
model_hypo2 = brm(
  MAD_abs_s ~ trial_type +
    (trial_type || subject_id)+
    (1|exemplar),
  control=list(adapt_delta=0.99, max_treedepth=15), 
  data = animal,
  prior = prior_hypo2
  )

#looking at model
model_hypo2

```

```{r}
#fitting model to actual data
pp_check(model_hypo2)
```

```{r}
# Extract the posteriors
posteriors2_trial_type <- model_hypo2 %>%
  spread_draws(b_Intercept, 
               b_trial_typeTypical) %>%
  # calculate posteriors for each individual level
  mutate(Atypical = b_Intercept,
         Typical = b_Intercept + b_trial_typeTypical) %>% 
  select(Atypical, Typical) %>% 
  gather(key = "parameter", value = "posterior") %>% 
  group_by(parameter) %>% 
  summarise(mean_posterior = mean(posterior),
            `95lowerCrI` = HDInterval::hdi(posterior, credMass = 0.90)[1],
            `95higherCrI` = HDInterval::hdi(posterior, credMass = 0.90)[2])
  
posteriors2_trial_type

# Extract the posteriors
posteriors2 <- model_hypo2 %>%
  spread_draws(b_trial_typeTypical) %>%
  select(b_trial_typeTypical) %>% 
  gather(key = "parameter", value = "posterior")  

  
posteriors2

```

```{r}
  
# plot
ggplot(data = posteriors2_trial_type, 
       aes(x = parameter, y = mean_posterior,
           color = parameter, fill = parameter)) + 
  geom_errorbar(aes(ymin = `95lowerCrI`, ymax = `95higherCrI`),
                width = 0.2, color = "grey") +
  geom_line(aes(group = 1), color = "black") +
  geom_point(size = 4) +
  labs(x = "trial_type",
       y = "posterior MAD scaled")

# plot the regression coefficients
  ggplot(posteriors2, aes(x = posterior, y = parameter)) + 
    # plot density 
    geom_halfeyeh(.width = 0.95) +
    # add axes titles
    xlab("\nMAD") +
    ylab("") +
    # adjust the x-axis 
    scale_x_continuous(limits = c(-10,10)) +
    # add line for the value zero
    geom_segment(x = 0, xend = 0, y = Inf, yend = -Inf,
                 lty = "dashed")

```

Results: MAD values are higher for Atypical than Typical trial types, due to the negative slope going from the reference level (Atypical) to the Typical trial type. The credible interval of the coefficient trial_typeTypical includes 0, wherefore there is no compelling evidence for the hypothesis to hold true. 



Hypothesis 3
```{r}

animal$mousetrackingDuration_s = my_scale(animal$mousetrackingDuration)

#informative prior
prior_hypo3 <- c(
  #priors for all fixed effects (trial_type)
  set_prior("student_t(3, 0, 300)", class = "b"),
  #prior for the Intercept
  set_prior("student_t(3, 1000, 300)", class = "Intercept"),
  #prior for all SDs including the varying intercepts and slopes
  set_prior("student_t(3, 0, 300)", class = "sd")
)

#by-subject_id varying intercepts and varying 
#slope, without slope/intercept correlation
#by-exemplar varying intercept
model_hypo3 = brm(
  mousetrackingDuration_s ~ trial_type +
    (trial_type || subject_id)+
    (1|exemplar),
  control=list(adapt_delta=0.99, max_treedepth=15), 
  data = animal,
  prior = prior_hypo3
  )

model_hypo3


```

```{r}
#fitting the model to the actual data
pp_check(model_hypo3)

```


```{r}
# Extract the posteriors
posteriors3_trial_type <- model_hypo3 %>%
  spread_draws(b_Intercept, 
               b_trial_typeTypical) %>%
  # calculate posteriors for each individual level
  mutate(Atypical = b_Intercept,
         Typical = b_Intercept + b_trial_typeTypical) %>% 
  select(Atypical, Typical) %>% 
  gather(key = "parameter", value = "posterior") %>% 
  group_by(parameter) %>% 
  summarise(mean_posterior = mean(posterior),
            `95lowerCrI` = HDInterval::hdi(posterior, credMass = 0.90)[1],
            `95higherCrI` = HDInterval::hdi(posterior, credMass = 0.90)[2])
  
posteriors3_trial_type

# Extract the posteriors
posteriors3 <- model_hypo3 %>%
  spread_draws(b_trial_typeTypical) %>%
  select(b_trial_typeTypical) %>% 
  gather(key = "parameter", value = "posterior")  

  
posteriors3
```


```{r}
# plot
ggplot(data = posteriors3_trial_type, 
       aes(x = parameter, y = mean_posterior,
           color = parameter, fill = parameter)) + 
  geom_errorbar(aes(ymin = `95lowerCrI`, ymax = `95higherCrI`),
                width = 0.2, color = "grey") +
  geom_line(aes(group = 1), color = "black") +
  geom_point(size = 4) +
  labs(x = "trial_type",
       y = "posterior mousetrackingDuration scaled")

# plot the regression coefficients
  ggplot(posteriors3, aes(x = posterior, y = parameter)) + 
    # plot density 
    geom_halfeyeh(.width = 0.95) +
    # add axes titles
    xlab("\nmousetrackingDuration") +
    ylab("") +
    # adjust the x-axis 
    scale_x_continuous(limits = c(-10,10)) +
    # add line for the value zero
    geom_segment(x = 0, xend = 0, y = Inf, yend = -Inf,
                 lty = "dashed")

```

Results: The mousetracking duration values are higher for Atypical than Typical trial types, due to the negative slope going from the reference level (Atypical) to the Typical trial type. The credible interval of the coefficient trial_typeTypical includes 0, wherefore there is no compelling evidence for the hypothesis to hold true.


Hypothesis 4
```{r}

animal$factor_prototype_label <- factor(animal$prototype_label)

class(animal$factor_prototype_label)


#multinomial logistic regression model 
#by-subject_id varying intercepts and varying 
#slope, without slope/intercept correlation
#by-exemplar varying intercept
model_hypo4 <- brm(
  factor_prototype_label ~ trial_type +
    (trial_type || subject_id)+
    (1|exemplar),
  data = animal,
  family = categorical(link = "logit", refcat = NULL)
)

model_hypo4


```


```{r}
#fitting the model to the actual data
pp_check(model_hypo4)
```

```{r}
marginal_effects(model_hypo4, "trial_type", categorical = TRUE)
```

```{r}
#extracting posteriors
predicted_hypo4 <- model_hypo4 %>%
  spread_draws(b_mucurved_Intercept,
               b_mudCoM_Intercept,
               b_mustraight_Intercept ,
               b_mucurved_trial_typeTypical,
               b_mudCoM_trial_typeTypical,
               b_mustraight_trial_typeTypical) %>%
  # mutating the parameters with their coefficient combination
  mutate(curved_Atypical = plogis(b_mucurved_Intercept),
         curved_Typical = plogis(b_mucurved_Intercept + b_mucurved_trial_typeTypical),
         dCoM_Atypical = plogis(b_mudCoM_Intercept),
          dCoM_Typical = plogis(b_mudCoM_Intercept + b_mudCoM_trial_typeTypical),
         straight_Atypical = plogis(b_mustraight_Intercept),
         straight_Typical = plogis(b_mustraight_Intercept + b_mustraight_trial_typeTypical),
         cCoM_Atypical = plogis(b_mucurved_Intercept + b_mudCoM_Intercept + b_mustraight_Intercept),
         cCoM_Typical = plogis(b_mucurved_Intercept + b_mudCoM_Intercept + b_mustraight_Intercept + b_mucurved_trial_typeTypical +
                             b_mudCoM_trial_typeTypical + b_mustraight_trial_typeTypical)) %>%
  select(curved_Atypical, curved_Typical, dCoM_Atypical, dCoM_Typical, straight_Atypical, straight_Typical, cCoM_Atypical, cCoM_Typical) %>% 
  gather(key = "parameter", value = "posterior") %>% 
  #muatating categories for cluster and condition for better plotting 
   mutate(prototype = ifelse(parameter == "curved_Atypical" | parameter == "curved_Typical",
                        "curved",ifelse(parameter == "dCoM_Atypical"|parameter == "dCoM_Typical", "dcom", ifelse(parameter == "straight_Atypical"|parameter == "straight_Typical", "straight", "cCoM"))),
          trial_type = ifelse(parameter == "curved_Atypical" | parameter == "dCoM_Atypical" | parameter == "straight_Atypical" | parameter == "cCoM_Atypical",
                        "Atypical", "Typical")) %>%
  group_by(prototype, trial_type) %>%
  summarise(mean_posterior = mean(posterior),
            `95lowerCrI` = HDInterval::hdi(posterior, credMass = 0.90)[1],
            `95higherCrI` = HDInterval::hdi(posterior, credMass = 0.90)[2])

predicted_hypo4


```


```{r}
#plotting mean posterior probability of every prototype for each trial type
ggplot(predicted_hypo4) +
   geom_errorbar(aes(x = trial_type, y = mean_posterior, color = prototype,
                    ymin = `95lowerCrI`, ymax = `95higherCrI`),
                width = 0.2,  position = position_dodge(width = 0.6)) +
  geom_point(aes(x = trial_type, y = mean_posterior, fill = prototype),
             size = 4, pch = 21, color = "black", position = position_dodge(0.6)) 

```


Results: The graph indicates that the mean posterior probabilities of the prototypes are higher for the Atypical trial compared to all mean posterior probabilities of the prototypes for the Typical trial type. Therefore we can assume that the likelihood of obtaining different cluster types depends on the experimental condition. 

Hypothese 5
```{r}
animal$RT_log <- log(animal$RT)
animal$RT_log_s = my_scale(animal$RT_log)

#informative priors
prior_hypo5 <- c(
  #priors for all fixed effects (trial_type)
  set_prior("student_t(3, 7, 2.5)", class = "b"),
  #prior for the Intercept
  set_prior("student_t(3, 0, 2)", class = "Intercept"),
  #prior for all SDs including the varying intercepts and slopes
  set_prior("student_t(3, 0, 2)", class = "sd")
)

#by-subject_id varying intercepts and varying 
#slope, without slope/intercept correlation
#by-exemplar varying intercept
model_hypo5 = brm(
  RT_log_s ~ trial_type +
    (trial_type || subject_id)+
    (1 |exemplar),
  control=list(adapt_delta=0.99, max_treedepth=15), 
  data = animal,
  prior = prior_hypo5
  )


model_hypo5



```


```{r}
#fitting the model to the actual data
pp_check(model_hypo5)

```

```{r}

# Extract the posteriors
posteriors5_trial_type <- model_hypo5 %>%
  spread_draws(b_Intercept, 
               b_trial_typeTypical) %>%
  # calculate posteriors for each individual level
  mutate(Atypical = b_Intercept,
         Typical = b_Intercept + b_trial_typeTypical) %>% 
  select(Atypical, Typical) %>% 
  gather(key = "parameter", value = "posterior") %>% 
  group_by(parameter) %>% 
  summarise(mean_posterior = mean(posterior),
            `95lowerCrI` = HDInterval::hdi(posterior, credMass = 0.90)[1],
            `95higherCrI` = HDInterval::hdi(posterior, credMass = 0.90)[2])
  
posteriors5_trial_type

# Extract the posteriors
posteriors5 <- model_hypo5 %>%
  spread_draws(b_trial_typeTypical) %>%
  select(b_trial_typeTypical) %>% 
  gather(key = "parameter", value = "posterior")  

  
posteriors5
```

```{r}

# plot
ggplot(data = posteriors5_trial_type, 
       aes(x = parameter, y = mean_posterior,
           color = parameter, fill = parameter)) + 
  geom_errorbar(aes(ymin = `95lowerCrI`, ymax = `95higherCrI`),
                width = 0.2, color = "grey") +
  geom_line(aes(group = 1), color = "black") +
  geom_point(size = 4) +
  labs(x = "trial_type",
       y = "posterior RT_log scaled")

# plot the regression coefficients
  ggplot(posteriors5, aes(x = posterior, y = parameter)) + 
    # plot density 
    geom_halfeyeh(.width = 0.95) +
    # add axes titles
    xlab("\nRT_log") +
    ylab("") +
    # adjust the x-axis 
    scale_x_continuous(limits = c(-10,10)) +
    # add line for the value zero
    geom_segment(x = 0, xend = 0, y = Inf, yend = -Inf,
                 lty = "dashed")

```

Results: The scales RT_log values are higher for Atypical than Typical trial types, due to the negative slope going from the reference level (Atypical) to the Typical trial type. The credible interval of the coefficient trial_typeTypical includes 0, wherefore there is no compelling evidence for the hypothesis to hold true.

Hypothesis 6
```{r}

#informative prior
prior_hypo6 <- c(
  #priors for all fixed effects (trial_type)
  set_prior("student_t(3, 300, 400)", class = "b"),
  #prior for the Intercept
  set_prior("student_t(3, 0,400)", class = "Intercept"),
  #prior for all SDs including the varying intercepts and slopes
  set_prior("student_t(3, 0, 400)", class = "sd"),
  set_prior("student_t(3, 0, 400)", class = "sigma")
)

#by-subject_id varying intercepts and varying 
#slope, without slope/intercept correlation
#by-exemplar varying intercept
model_hypo6 = brm(
  initiation_time ~ trial_type +
    (trial_type || subject_id)+
    (1 |exemplar),
  control=list(adapt_delta=0.99, max_treedepth=15), 
  data = animal,
  prior = prior_hypo6
  )


model_hypo6


```

```{r}
#fitting the model to the actual data
pp_check(model_hypo6)

```

```{r}

# Extract the posteriors
posteriors6_trial_type <- model_hypo6 %>%
  spread_draws(b_Intercept, 
               b_trial_typeTypical) %>%
  # calculate posteriors for each individual level
  mutate(Atypical = b_Intercept,
         Typical = b_Intercept + b_trial_typeTypical) %>% 
  select(Atypical, Typical) %>% 
  gather(key = "parameter", value = "posterior") %>% 
  group_by(parameter) %>% 
  summarise(mean_posterior = mean(posterior),
            `95lowerCrI` = HDInterval::hdi(posterior, credMass = 0.90)[1],
            `95higherCrI` = HDInterval::hdi(posterior, credMass = 0.90)[2])
  
posteriors6_trial_type

# Extract the posteriors
posteriors6 <- model_hypo6 %>%
  spread_draws(b_trial_typeTypical) %>%
  select(b_trial_typeTypical) %>% 
  gather(key = "parameter", value = "posterior")  

  
posteriors6


```

```{r}
 
# plot
ggplot(data = posteriors6_trial_type, 
       aes(x = parameter, y = mean_posterior,
           color = parameter, fill = parameter)) + 
  geom_errorbar(aes(ymin = `95lowerCrI`, ymax = `95higherCrI`),
                width = 0.2, color = "grey") +
  geom_line(aes(group = 1), color = "black") +
  geom_point(size = 4) +
  labs(x = "trial_type",
       y = "posterior initiation time")

# plot the regression coefficients
  ggplot(posteriors6, aes(x = posterior, y = parameter)) + 
    # plot density 
    geom_halfeyeh(.width = 0.95) +
    # add axes titles
    xlab("\nInitiation Time") +
    ylab("") +
    # adjust the x-axis 
    scale_x_continuous(limits = c(-5000,5000)) +
    # add line for the value zero
    geom_segment(x = 0, xend = 0, y = Inf, yend = -Inf,
                 lty = "dashed")

```

Results: The initiation time values are lower for Atypical than Typical trial types, due to the positive slope going from the reference level (Atypical) to the Typical trial type. The credible interval of the coefficient trial_typeTypical includes 0, wherefore there is no compelling evidence for the hypothesis to hold true.


Hypothese 7
```{r}
animal$traveledDistance_abs <- abs(animal$traveledDistance)

#informative prior
prior_hypo7 <- c(
  #prior for the Intercept
  set_prior("student_t(3, 50,10)", class = "Intercept"),
  #prior for all SDs including the varying intercepts and slopes
  set_prior("student_t(3, 0, 10)", class = "sd"),
  set_prior("student_t(3, 0, 10)", class = "sigma")
)

#by-subject_id varying intercepts and varying 
#slope, without slope/intercept correlation
#by-exemplar varying intercept
model_hypo7 = brm(
  traveledDistance_abs ~ trial_type +
    (trial_type || subject_id)+
    (1 |exemplar),
  control=list(adapt_delta=0.99, max_treedepth=15), 
  data = animal,
  prior = prior_hypo7
  )


model_hypo7

```


```{r}
#fitting the model to the actual data
pp_check(model_hypo7)

```

```{r}

# Extract the posteriors
posteriors7_trial_type <- model_hypo7 %>%
  spread_draws(b_Intercept, 
               b_trial_typeTypical) %>%
  # calculate posteriors for each individual level
  mutate(Atypical = b_Intercept,
         Typical = b_Intercept + b_trial_typeTypical) %>% 
  select(Atypical, Typical) %>% 
  gather(key = "parameter", value = "posterior") %>% 
  group_by(parameter) %>% 
  summarise(mean_posterior = mean(posterior),
            `95lowerCrI` = HDInterval::hdi(posterior, credMass = 0.90)[1],
            `95higherCrI` = HDInterval::hdi(posterior, credMass = 0.90)[2])
  
posteriors7_trial_type

# Extract the posteriors
posteriors7 <- model_hypo7 %>%
  spread_draws(b_trial_typeTypical) %>%
  select(b_trial_typeTypical) %>% 
  gather(key = "parameter", value = "posterior")  

  
posteriors7

posterior7_agg <- posteriors7 %>% 
  mutate(mean_posterior = mean(posterior))

posterior7_agg


```

```{r}
 
# plot
ggplot(data = posteriors7_trial_type, 
       aes(x = parameter, y = mean_posterior,
           color = parameter, fill = parameter)) + 
  geom_errorbar(aes(ymin = `95lowerCrI`, ymax = `95higherCrI`),
                width = 0.2, color = "grey") +
  geom_line(aes(group = 1), color = "black") +
  geom_point(size = 4) +
  labs(x = "trial_type",
       y = "posterior traveled Distance")

# plot the regression coefficients
  ggplot(posteriors7, aes(x = posterior, y = parameter)) + 
    # plot density 
    geom_halfeyeh(.width = 0.95) +
    # add axes titles
    xlab("\n Traveled Distance") +
    ylab("") +
    # adjust the x-axis 
    scale_x_continuous(limits = c(-500,500)) +
    # add line for the value zero
    geom_segment(x = 0, xend = 0, y = Inf, yend = -Inf,
                 lty = "dashed")

#computing evidential ratio and posterior probability  
hypothesis(model_hypo7, "trial_typeTypical > -25.60")

```

Results: The initiation time values are higher for Atypical than Typical trial types, due to the negative slope going from the reference level (Atypical) to the Typical trial type. The credible interval of the coefficient trial_typeTypical does not includes 0, wherefore there is evidence for the hypothesis to hold true. The evidence ratio is 1.03 and the posterior probability is 51%. This means that the strength of evidence is barely worth mentioning. 


