---
title: "Capital Study: Data Cleaning"
author:  "Group 10"
output: 
  html_document:
    toc: true
    toc_depth: 2
    highlight: tango
---
```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, error = F, message = F, warning = F)

```

```{r libraries, include=FALSE, message=FALSE, warning=FALSE}

# package for convenience functions (e.g. ggplot2, dplyr, etc.)
library(tidyverse)

# package for Bayesian regression modeling
library(brms)

# package for visualization
library(tidybayes)

# package to visualize 
library(bayesplot)

# package to extract HDIs
library(HDInterval)

# these options help Stan run faster
options(mc.cores = parallel::detectCores())

#devtools::install_github("michael-franke/aida-package")
library(aida)

# communication with Stan
library(rstan)


# use the aida-theme for plotting
theme_set(theme_aida())

# global color scheme / non-optimized
project_colors = c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#000000")

# setting theme colors globally
scale_colour_discrete <- function(...) {
  scale_colour_manual(..., values = project_colors)
}
scale_fill_discrete <- function(...) {
   scale_fill_manual(..., values = project_colors)
} 

# define scale function to avoid matrix object in tibble
my_scale <- function(x) c(scale(x))

```

```{r}
#loading for analysis prepared data table
capital <- read.csv("capital_data.csv")

```

##Data Analysis - Original Study 

For the main trials of our experiment we hold the following research hypotheses:

H1: The area under the curve (AUC) is larger for atypical trials compared to typical trials.

H2: The maximal absolute deviation (MAD) is larger for atypical trials compared to typical trials.

H3: Movement duration is longer for atypical trials compared to typical trials.

H4: The likelihood of obtaining different cluster types depends on the experimental conditions.

H5: The total categorisation response time is longer for atypical trials compared to typical trials.

H6: The movement initiation latency is longer for atypical trials compared to typical trials.

H7: The distance travelled in pixels is longer for atypical trials compared to typical trials.

#REGRESSION MODELS

Hypothesis 1
```{r}
#Taking absolute AUC values, since negative AUC make no sense
capital$AUC_abs = abs(capital$AUC)
capital$AUC_abs_s = my_scale(capital$AUC_abs)

#informative prior
prior_hypo1 <- c(
  #priors for all fixed effects (trial_type)
  set_prior("student_t(3, 0, 2)", class = "sd"),
  #prior for the Intercept
  set_prior("student_t(3, 0, 2)", class = "Intercept"),
  #prior for all SDs including the varying intercepts and slopes
  set_prior("student_t(3, 0, 2)", class = "sigma")
)

#by-subject_id varying intercepts and varying 
#slope, without slope/intercept correlation
#by-exemplar varying intercept
model_hypo1 = brm(
  AUC_abs_s ~ trial_type +
    (trial_type || subject_id)+
    (1 |exemplar),
  control=list(adapt_delta=0.99, max_treedepth=15), 
  data = capital,
  prior = prior_hypo1
  )

model_hypo1
```

```{r}
#fitting the model to the actual data
pp_check(model_hypo1)

```

```{r}
# Extract the posteriors
posteriors1_trial_type <- model_hypo1 %>%
  spread_draws(b_Intercept, 
               b_trial_typeTypical) %>%
  # calculate posteriors for each individual level
  mutate(Atypical = b_Intercept,
         Typical = b_Intercept + b_trial_typeTypical) %>% 
  select(Atypical, Typical) %>% 
  gather(key = "parameter", value = "posterior") %>% 
  group_by(parameter) %>% 
  summarise(mean_posterior = mean(posterior),
            `95lowerCrI` = HDInterval::hdi(posterior, credMass = 0.90)[1],
            `95higherCrI` = HDInterval::hdi(posterior, credMass = 0.90)[2])
  
posteriors1_trial_type

# Extract the posteriors
posteriors1 <- model_hypo1 %>%
  spread_draws(b_trial_typeTypical) %>%
  select(b_trial_typeTypical) %>% 
  gather(key = "parameter", value = "posterior")  

  
posteriors1

posterior1_agg <- posteriors1 %>% 
  mutate(mean_posterior = mean(posterior))

posterior1_agg
```

```{r}

# plot
ggplot(data = posteriors1_trial_type, 
       aes(x = parameter, y = mean_posterior,
           color = parameter, fill = parameter)) + 
  geom_errorbar(aes(ymin = `95lowerCrI`, ymax = `95higherCrI`),
                width = 0.2, color = "grey") +
  geom_line(aes(group = 1), color = "black") +
  geom_point(size = 4) +
  labs(x = "trial_type",
       y = "posterior AUC scaled")

# plot the regression coefficients
  ggplot(posteriors1, aes(x = posterior, y = parameter)) + 
    # plot density 
    geom_halfeyeh(.width = 0.95) +
    # add axes titles
    xlab("\nAUC") +
    ylab("") +
    # adjust the x-axis 
    scale_x_continuous(limits = c(-10,10)) +
    # add line for the value zero
    geom_segment(x = 0, xend = 0, y = Inf, yend = -Inf,
                 lty = "dashed")
  
```

Results: The mean posterior scaled AUC values are for both trial types almost the same. The credible interval of the coefficient trial_typeTypical includes 0, wherefore there is no compelling evidence for the hypothesis to hold true. 

Hypothesis 2
```{r}
#Taking absolute AUC values, since negative AUC make no sense
capital$MAD_abs = abs(capital$MAD)
capital$MAD_abs_s = my_scale(capital$MAD_abs)

#informative prior
prior_hypo2 <- c(
  #priors for all fixed effects (trial_type)
  set_prior("student_t(3, 0, 2)", class = "sigma"),
  #prior for the Intercept
  set_prior("student_t(3, 0, 2)", class = "Intercept"),
  #prior for all SDs including the varying intercepts and slopes
  set_prior("student_t(3, 0, 2)", class = "sd")
)

#by-subject_id varying intercepts and varying 
#slope, without slope/intercept correlation
#by-exemplar varying intercept
model_hypo2 = brm(
  MAD_abs_s ~ trial_type +
    (trial_type || subject_id)+
    (1|exemplar),
  control=list(adapt_delta=0.99, max_treedepth=15), 
  data = capital,
  prior = prior_hypo2
  )

model_hypo2

```

```{r}
#fitting the model to the actual data
pp_check(model_hypo2)
```

```{r}
# Extract the posteriors
posteriors2_trial_type <- model_hypo2 %>%
  spread_draws(b_Intercept, 
               b_trial_typeTypical) %>%
  # calculate posteriors for each individual level
  mutate(Atypical = b_Intercept,
         Typical = b_Intercept + b_trial_typeTypical) %>% 
  select(Atypical, Typical) %>% 
  gather(key = "parameter", value = "posterior") %>% 
  group_by(parameter) %>% 
  summarise(mean_posterior = mean(posterior),
            `95lowerCrI` = HDInterval::hdi(posterior, credMass = 0.90)[1],
            `95higherCrI` = HDInterval::hdi(posterior, credMass = 0.90)[2])
  
posteriors2_trial_type

# Extract the posteriors
posteriors2 <- model_hypo2 %>%
  spread_draws(b_trial_typeTypical) %>%
  select(b_trial_typeTypical) %>% 
  gather(key = "parameter", value = "posterior")  

  
posteriors2

posterior2_agg <- posteriors2 %>% 
  mutate(mean_posterior = mean(posterior))

posterior2_agg

```

```{r}

# plot
ggplot(data = posteriors2_trial_type, 
       aes(x = parameter, y = mean_posterior,
           color = parameter, fill = parameter)) + 
  geom_errorbar(aes(ymin = `95lowerCrI`, ymax = `95higherCrI`),
                width = 0.2, color = "grey") +
  geom_line(aes(group = 1), color = "black") +
  geom_point(size = 4) +
  labs(x = "trial_type",
       y = "posterior MAD scaled")

# plot the regression coefficients
  ggplot(posteriors2, aes(x = posterior, y = parameter)) + 
    # plot density 
    geom_halfeyeh(.width = 0.95) +
    # add axes titles
    xlab("\nMAD") +
    ylab("") +
    # adjust the x-axis 
    scale_x_continuous(limits = c(-10,10)) +
    # add line for the value zero
    geom_segment(x = 0, xend = 0, y = Inf, yend = -Inf,
                 lty = "dashed")

```

Results: Absolute scaled mean posterior MAD values are higher for Atypical than Typical trial types, due to the negative slope going from the reference level (Atypical) to the Typical trial type. The credible interval of the coefficient trial_typeTypical includes 0, wherefore there is no compelling evidence for the hypothesis to hold true.


Hypothesis 3
```{r}

capital$mousetrackingDuration_s = my_scale(capital$mousetrackingDuration)

#informative prior
prior_hypo3 <- c(
  #priors for all fixed effects (trial_type)
  set_prior("student_t(3, 0, 2)", class = "sigma"),
  #prior for the Intercept
  set_prior("student_t(3, 0, 2)", class = "Intercept"),
  #prior for all SDs including the varying intercepts and slopes
  set_prior("student_t(3, 0, 2)", class = "sd")
)

#by-subject_id varying intercepts and varying 
#slope, without slope/intercept correlation
#by-exemplar varying intercept
model_hypo3 = brm(
  mousetrackingDuration_s ~ trial_type +
    (trial_type || subject_id)+
    (1|exemplar),
  control=list(adapt_delta=0.99, max_treedepth=15), 
  data = capital,
  prior = prior_hypo3
  )

model_hypo3


```

```{r}
#fitting the model to the actual data
pp_check(model_hypo3)

```


```{r}
# Extract the posteriors
posteriors3_trial_type <- model_hypo3 %>%
  spread_draws(b_Intercept, 
               b_trial_typeTypical) %>%
  # calculate posteriors for each individual level
  mutate(Atypical = b_Intercept,
         Typical = b_Intercept + b_trial_typeTypical) %>% 
  select(Atypical, Typical) %>% 
  gather(key = "parameter", value = "posterior") %>% 
  group_by(parameter) %>% 
  summarise(mean_posterior = mean(posterior),
            `95lowerCrI` = HDInterval::hdi(posterior, credMass = 0.90)[1],
            `95higherCrI` = HDInterval::hdi(posterior, credMass = 0.90)[2])
  
posteriors3_trial_type

# Extract the posteriors
posteriors3 <- model_hypo3 %>%
  spread_draws(b_trial_typeTypical) %>%
  select(b_trial_typeTypical) %>% 
  gather(key = "parameter", value = "posterior")  

  
posteriors3

posterior3_agg <- posteriors3 %>% 
  mutate(mean_posterior = mean(posterior))

posterior3_agg


```


```{r}

# plot
ggplot(data = posteriors3_trial_type, 
       aes(x = parameter, y = mean_posterior,
           color = parameter, fill = parameter)) + 
  geom_errorbar(aes(ymin = `95lowerCrI`, ymax = `95higherCrI`),
                width = 0.2, color = "grey") +
  geom_line(aes(group = 1), color = "black") +
  geom_point(size = 4) +
  labs(x = "trial_type",
       y = "posterior mousetrackingDuration scaled")

# plot the regression coefficients
  ggplot(posteriors3, aes(x = posterior, y = parameter)) + 
    # plot density 
    geom_halfeyeh(.width = 0.95) +
    # add axes titles
    xlab("\nmousetrackingDuration") +
    ylab("") +
    # adjust the x-axis 
    scale_x_continuous(limits = c(-10,10)) +
    # add line for the value zero
    geom_segment(x = 0, xend = 0, y = Inf, yend = -Inf,
                 lty = "dashed")
  
#computing evidential ratio and posterior probability  
hypothesis(model_hypo3, "trial_typeTypical > -0.67")  
  
```

Results: Scaled mean posterior mousetracking Duration values are higher for Atypical than Typical trial types, due to the negative slope going from the reference level (Atypical) to the Typical trial type. The credible interval of the coefficient trial_typeTypical does not include 0, wherefore there is compelling evidence for the hypothesis to hold true. The credible interval values are however very close to 0. The evidence ratio for the hypothesis to hold true is 0.94 and the posterior probability is 48%. Because both of the values are small, we can assume that the evidence for the hypothesis to hold true is not noteworthy.

Hypothesis 4
```{r}

capital$factor_prototype_label <- factor(capital$prototype_label)

#multinomial logistic regression model 
#by-subject_id varying intercepts and varying 
#slope, without slope/intercept correlation
#by-exemplar varying intercept
model_hypo4 <- brm(
  factor_prototype_label ~ trial_type +
    (trial_type || subject_id)+
    (1|exemplar),
  data = capital,
  family = categorical(link = "logit", refcat = NULL)
)

model_hypo4


```





```{r}
#fitting model to the actual data
pp_check(model_hypo4)
```

```{r}
#plotting marginal probabilities 
marginal_effects(model_hypo4, "trial_type", categorical = TRUE)
```

```{r}
#extracting posteriors
predicted_hypo4 <- model_hypo4 %>%
  spread_draws(b_mucurved_Intercept,
               b_mudCoM_Intercept,
               b_mustraight_Intercept,
               b_mudCoM2_Intercept,
               b_mucurved_trial_typeTypical,
               b_mudCoM_trial_typeTypical,
               b_mustraight_trial_typeTypical,
               b_mudCoM2_trial_typeTypical) %>%
  # mutating the parameters with their coefficient combination
  mutate(curved_Atypical = plogis(b_mucurved_Intercept),
         curved_Typical = plogis(b_mucurved_Intercept + b_mucurved_trial_typeTypical),
         dCoM_Atypical = plogis(b_mudCoM_Intercept),
          dCoM_Typical = plogis(b_mudCoM_Intercept + b_mudCoM_trial_typeTypical),
         straight_Atypical = plogis(b_mustraight_Intercept),
         straight_Typical = plogis(b_mustraight_Intercept + b_mustraight_trial_typeTypical),
         dCoM2_Atypical = plogis(b_mudCoM2_Intercept),
          dCoM2_Typical = plogis(b_mudCoM2_Intercept + b_mudCoM2_trial_typeTypical),
         cCoM_Atypical = plogis(b_mucurved_Intercept + b_mudCoM_Intercept + b_mustraight_Intercept + b_mudCoM2_Intercept),
         cCoM_Typical = plogis(b_mucurved_Intercept + b_mudCoM_Intercept + b_mustraight_Intercept + b_mucurved_trial_typeTypical +
                             b_mudCoM_trial_typeTypical + b_mustraight_trial_typeTypical + b_mudCoM2_Intercept + b_mudCoM2_trial_typeTypical)) %>%
  select(curved_Atypical, curved_Typical, dCoM_Atypical, dCoM_Typical, dCoM2_Atypical, dCoM2_Typical, straight_Atypical, straight_Typical, cCoM_Atypical, cCoM_Typical) %>% 
  gather(key = "parameter", value = "posterior") %>% 
  #muatating categories for cluster and condition for better plotting 
   mutate(prototype = ifelse(parameter == "curved_Atypical" | parameter == "curved_Typical",
                        "curved",ifelse(parameter == "dCoM_Atypical"|parameter == "dCoM_Typical", "dCoM", ifelse(parameter == "straight_Atypical"|parameter == "straight_Typical", "straight", ifelse(parameter == "dCoM2_Atypical" | parameter == "dCoM2_Typical",
                        "dCoM2", "cCoM")))),
          trial_type = ifelse(parameter == "curved_Atypical" | parameter == "dCoM_Atypical" | parameter == "straight_Atypical" | parameter == "cCoM_Atypical"| parameter == "dCoM2_Atypical",
                        "Atypical", "Typical")) %>%
  group_by(prototype, trial_type) %>%
  summarise(mean_posterior = mean(posterior),
            `95lowerCrI` = HDInterval::hdi(posterior, credMass = 0.90)[1],
            `95higherCrI` = HDInterval::hdi(posterior, credMass = 0.90)[2])

predicted_hypo4


```


```{r}
#plotting mean posterior probability of every prototype for each trial type
ggplot(predicted_hypo4) +
   geom_errorbar(aes(x = trial_type, y = mean_posterior, color = prototype,
                    ymin = `95lowerCrI`, ymax = `95higherCrI`),
                width = 0.2,  position = position_dodge(width = 0.6)) +
  geom_point(aes(x = trial_type, y = mean_posterior, fill = prototype),
             size = 4, pch = 21, color = "black", position = position_dodge(0.6)) 


```

Results: The graph indicates the mean posterior probabilities of the prototypes for each trial type.Taking from the graph there are no big differences between the prototype occuerences of trial types. For the prototype straight the mean posteriors are the highest in both trial types. Overall no noteworthy influence of the experimental condition can be seen on the likelihood of obtaining different amounts of prototypes.  

Hypothese 5
```{r}
capital$RT_log <- log(capital$RT)
capital$RT_log_s = my_scale(capital$RT_log)

#informative priors
prior_hypo5 <- c(
  #priors for all fixed effects (trial_type)
  set_prior("student_t(3, 0, 2)", class = "sigma"),
  #prior for the Intercept
  set_prior("student_t(3, 7, 2)", class = "Intercept"),
  #prior for all SDs including the varying intercepts and slopes
  set_prior("student_t(3, 0, 2)", class = "sd")
)

#by-subject_id varying intercepts and varying 
#slope, without slope/intercept correlation
#by-exemplar varying intercept
model_hypo5 = brm(
  RT_log ~ trial_type +
    (trial_type || subject_id)+
    (1 |exemplar),
  control=list(adapt_delta=0.99, max_treedepth=15), 
  data = capital,
  prior = prior_hypo5
  )


model_hypo5


```

```{r}
#fitting the model to the actual data
pp_check(model_hypo5)

```

```{r}

# Extract the posteriors
posteriors5_trial_type <- model_hypo5 %>%
  spread_draws(b_Intercept, 
               b_trial_typeTypical) %>%
  # calculate posteriors for each individual level
  mutate(Atypical = b_Intercept,
         Typical = b_Intercept + b_trial_typeTypical) %>% 
  select(Atypical, Typical) %>% 
  gather(key = "parameter", value = "posterior") %>% 
  group_by(parameter) %>% 
  summarise(mean_posterior = mean(posterior),
            `95lowerCrI` = HDInterval::hdi(posterior, credMass = 0.90)[1],
            `95higherCrI` = HDInterval::hdi(posterior, credMass = 0.90)[2])
  
posteriors5_trial_type

# Extract the posteriors
posteriors5 <- model_hypo5 %>%
  spread_draws(b_trial_typeTypical) %>%
  select(b_trial_typeTypical) %>% 
  gather(key = "parameter", value = "posterior")  

  
posteriors5

posterior5_agg <- posteriors5 %>% 
  mutate(mean_posterior = mean(posterior))

posterior5_agg


```

```{r}
# plot
ggplot(data = posteriors5_trial_type, 
       aes(x = parameter, y = mean_posterior,
           color = parameter, fill = parameter)) + 
  geom_errorbar(aes(ymin = `95lowerCrI`, ymax = `95higherCrI`),
                width = 0.2, color = "grey") +
  geom_line(aes(group = 1), color = "black") +
  geom_point(size = 4) +
  labs(x = "trial_type",
       y = "posterior RT_log scaled")

# plot the regression coefficients
  ggplot(posteriors5, aes(x = posterior, y = parameter)) + 
    # plot density 
    geom_halfeyeh(.width = 0.95) +
    # add axes titles
    xlab("\nRT_log") +
    ylab("") +
    # adjust the x-axis 
    scale_x_continuous(limits = c(-10,10)) +
    # add line for the value zero
    geom_segment(x = 0, xend = 0, y = Inf, yend = -Inf,
                 lty = "dashed")
  
#computing evidential ratio and posterior probability  
hypothesis(model_hypo5, "(trial_typeTypical) > -0.28")      

```

Results: Log-transformed and scaled mean posterior RT values are higher for Atypical than Typical trial types, due to the negative slope going from the reference level (Atypical) to the Typical trial type. The credible interval of the coefficient trial_typeTypical does not include 0, wherefore there is compelling evidence for the hypothesis to hold true.The evidence ratio for the hypothesis to hold true is 0.85 and the posterior probability is 46%. Because both of the values are small, we can assume that the evidence for the hypothesis to hold true is not noteworthy.

Hypothesis 6
```{r}
capital$initiation_time_s = my_scale(capital$initiation_time)

#informative priors
prior_hypo6 <- c(
  #prior for the Intercept
  set_prior("student_t(3, 0,2)", class = "Intercept"),
  #prior for all SDs including the varying intercepts and slopes
  set_prior("student_t(3, 0, 2)", class = "sd"),
  set_prior("student_t(3, 0, 2)", class = "sigma")
)

#by-subject_id varying intercepts and varying 
#slope, without slope/intercept correlation
#by-exemplar varying intercept
model_hypo6 = brm(
  initiation_time_s ~ trial_type +
    (trial_type || subject_id)+
    (1 |exemplar),
  control=list(adapt_delta=0.99, max_treedepth=15), 
  data = capital,
  prior = prior_hypo6
  )



model_hypo6
```

```{r}
#fitting the model to the actual data
pp_check(model_hypo6)

```

```{r}

# Extract the posteriors
posteriors6_trial_type <- model_hypo6 %>%
  spread_draws(b_Intercept, 
               b_trial_typeTypical) %>%
  # calculate posteriors for each individual level
  mutate(Atypical = b_Intercept,
         Typical = b_Intercept + b_trial_typeTypical) %>% 
  select(Atypical, Typical) %>% 
  gather(key = "parameter", value = "posterior") %>% 
  group_by(parameter) %>% 
  summarise(mean_posterior = mean(posterior),
            `95lowerCrI` = HDInterval::hdi(posterior, credMass = 0.90)[1],
            `95higherCrI` = HDInterval::hdi(posterior, credMass = 0.90)[2])
  
posteriors6_trial_type

# Extract the posteriors
posteriors6 <- model_hypo6 %>%
  spread_draws(b_trial_typeTypical) %>%
  select(b_trial_typeTypical) %>% 
  gather(key = "parameter", value = "posterior")  

  
posteriors6


posterior6_agg <- posteriors6 %>% 
  mutate(mean_posterior = mean(posterior))

posterior6_agg


```

```{r}
# plot
ggplot(data = posteriors6_trial_type, 
       aes(x = parameter, y = mean_posterior,
           color = parameter, fill = parameter)) + 
  geom_errorbar(aes(ymin = `95lowerCrI`, ymax = `95higherCrI`),
                width = 0.2, color = "grey") +
  geom_line(aes(group = 1), color = "black") +
  geom_point(size = 4) +
  labs(x = "trial_type",
       y = "posterior initiation time")

# plot the regression coefficients
  ggplot(posteriors6, aes(x = posterior, y = parameter)) + 
    # plot density 
    geom_halfeyeh(.width = 0.95) +
    # add axes titles
    xlab("\nInitiation Time") +
    ylab("") +
    # adjust the x-axis 
    scale_x_continuous(limits = c(-5,5)) +
    # add line for the value zero
    geom_segment(x = 0, xend = 0, y = Inf, yend = -Inf,
                 lty = "dashed")

#computing evidential ratio and posterior probability  
hypothesis(model_hypo6, "trial_typeTypical > -0.31")    
  
```

Results: The scaled mean posterior initiation time values are lower for Atypical than Typical trial types, due to the positive slope going from the reference level (Atypical) to the Typical trial type. The credible interval of the coefficient trial_typeTypical does not include 0, wherefore there is compelling evidence for the hypothesis to hold true.The evidence ratio for the hypothesis to hold true is 0.85 and the posterior probability is 46%. Because both of the values are small, we can assume that the evidence for the hypothesis to hold true is not noteworthy.

Hypothese 7
```{r}
capital$traveledDistance_abs <- abs(capital$traveledDistance)
capital$traveledDistance_abs_s <- my_scale(capital$traveledDistance_abs)

#informative prior
prior_hypo7 <- c(
  #prior for the Intercept
  set_prior("student_t(3, 0,2)", class = "Intercept"),
  #prior for all SDs including the varying intercepts and slopes
  set_prior("student_t(3, 0, 2)", class = "sd"),
  set_prior("student_t(3, 0, 2)", class = "sigma")
)

#by-subject_id varying intercepts and varying 
#slope, without slope/intercept correlation
#by-exemplar varying intercept
model_hypo7 = brm(
  traveledDistance_abs_s ~ trial_type +
    (trial_type || subject_id)+
    (1 |exemplar),
  control=list(adapt_delta=0.99, max_treedepth=15), 
  data = capital,
  prior = prior_hypo7
  )


model_hypo7

```


```{r}
#fitting the model to the actual data
pp_check(model_hypo7)

```

```{r}

# Extract the posteriors
posteriors7_trial_type <- model_hypo7 %>%
  spread_draws(b_Intercept, 
               b_trial_typeTypical) %>%
  # calculate posteriors for each individual level
  mutate(Atypical = b_Intercept,
         Typical = b_Intercept + b_trial_typeTypical) %>% 
  select(Atypical, Typical) %>% 
  gather(key = "parameter", value = "posterior") %>% 
  group_by(parameter) %>% 
  summarise(mean_posterior = mean(posterior),
            `95lowerCrI` = HDInterval::hdi(posterior, credMass = 0.90)[1],
            `95higherCrI` = HDInterval::hdi(posterior, credMass = 0.90)[2])
  
posteriors7_trial_type

# Extract the posteriors
posteriors7 <- model_hypo7 %>%
  spread_draws(b_trial_typeTypical) %>%
  select(b_trial_typeTypical) %>% 
  gather(key = "parameter", value = "posterior")  

  
posteriors7

posterior7_agg <- posteriors7 %>% 
  mutate(mean_posterior = mean(posterior))

posterior7_agg

```

```{r}

# plot
ggplot(data = posteriors7_trial_type, 
       aes(x = parameter, y = mean_posterior,
           color = parameter, fill = parameter)) + 
  geom_errorbar(aes(ymin = `95lowerCrI`, ymax = `95higherCrI`),
                width = 0.2, color = "grey") +
  geom_line(aes(group = 1), color = "black") +
  geom_point(size = 4) +
  labs(x = "trial_type",
       y = "posterior traveled Distance")

# plot the regression coefficients
  ggplot(posteriors7, aes(x = posterior, y = parameter)) + 
    # plot density 
    geom_halfeyeh(.width = 0.95) +
    # add axes titles
    xlab("\n Traveled Distance") +
    ylab("") +
    # adjust the x-axis 
    scale_x_continuous(limits = c(-5,5)) +
    # add line for the value zero
    geom_segment(x = 0, xend = 0, y = Inf, yend = -Inf,
                 lty = "dashed")
  
#computing evidential ratio and posterior probability  
hypothesis(model_hypo7, "trial_typeTypical > -0.27")  

```

Results: The scaled mean posterior traveled distance values are higher for Atypical than Typical trial types, due to the negative slope going from the reference level (Atypical) to the Typical trial type. The credible interval of the coefficient trial_typeTypical does not include 0, wherefore there is evidence for the hypothesis to hold true. The evidence ratio is 0.97 and the posterior probability is 49%. This means that the strength of evidence is barely worth mentioning. 
