---
title: 'Capital Study: Data Cleaning'
author:  "Group 10"
output: 
  html_document:
    toc: true
    toc_depth: 2
    highlight: tango
---


```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, error = F, message = F, warning = F)

```

```{r libraries, include=FALSE, message=FALSE, warning=FALSE}

# package for convenience functions (e.g. ggplot2, dplyr, etc.)
library(tidyverse)

# package for visualization
library(tidybayes)

#devtools::install_github("michael-franke/aida-package")
library(aida)

#for analysing mousetracking data
library(mousetrap)

#for bimodality check
library(psych)

# and our dataset, let's call it dolphin
dolphin <- aida::aidata

# use the aida-theme for plotting
theme_set(theme_aida())

# global color scheme / non-optimized
project_colors = c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#000000")

# setting theme colors globally
scale_colour_discrete <- function(...) {
  scale_colour_manual(..., values = project_colors)
}
scale_fill_discrete <- function(...) {
   scale_fill_manual(..., values = project_colors)
} 

# define scale function to avoid matrix object in tibble
my_scale <- function(x) c(scale(x))

```

##Data Cleaning and Exclusion Criteria 
- The final analysis will only concern itself with correct trials
- Excluding all left-handed participants
- Participants who make incorrect category judgements in all three practice trials will be discarded 
- Data of participants who only have an accuracy of 50% will not be taken into account
- Exclude all data from participants who complete the experiment in under 500 ms or take longer than 60000 ms
- Trials which contain more than three flips along the y-axis will be taken out from the analysis
- Exclude trail with seaturtle - (because we messed that one up)

```{r}
#import data 
xdata_raw <- read_delim("Results_Table_Main.csv", 
    ";", escape_double = FALSE, trim_ws = TRUE)


as.tibble(xdata_raw)

#filter out test trials and subjects from pilot study
xdata_new_capital <- xdata_raw %>% 
  subset(submission_id != "1993" & submission_id != "1992" & submission_id != "1991" & submission_id != "1990" & submission_id != "1989" &
           submission_id != "1611" & submission_id != "1640" & submission_id != "1641"
         & submission_id != "1642" & submission_id != "1643" & submission_id != "1644")


```

##Original Experiment: Animal Data 

#DATA EXCLUSION

```{r}
##1. Excluding all left-handed participants

#create handedness table to merge with actual data 
#necessary in order to filter out left handed participants
xdata_handedness <- xdata_new_capital %>% 
  select(submission_id, response, trial_name) %>% 
  filter(trial_name == "mouse_question" | trial_name == "hand_question") %>% 
  spread(trial_name, response)  
   
xdata_handedness

##2. Participants who make incorrect category judgements in all three practice trials will be discarded 

#creating table to discard subjects who failed all 3 training trials
xdata_training_correct <- xdata_new_capital %>% 
  select(submission_id, correctness, trial_name) %>% 
    group_by(correctness, submission_id) %>% 
  filter(trial_name == "training") %>% 
  #count the amount of incorrect trials 
  count(failed = correctness == "Incorrect") %>% 
  #showing all subjects who failed all training trials
  subset(failed == "TRUE" & n != 3)

#there are no participants that failed all training trials   
xdata_training_correct  



#taking only the relevant participants for the pilot study 
#excluding left-handed participants
#only taking main trials
xdata_main <- xdata_new_capital %>% 
  #we only take the data from the capital study
  filter(correct == "Capital" | correct == "Non-Capital") %>% 
  #merge xdata with xdata_handedness
  full_join(xdata_handedness) %>% 
  #take all right handed participants
  filter(hand_question == "Right") 
 

xdata_main

##3. Data of participants who only have an accuracy of 50% will not be taken into account


#creating table to discard subjects who failed 50% of the answers 
xdata_wrong <- xdata_new_capital %>% 
  #take submission_id to see which subject failed 50% of the answers
  group_by(submission_id) %>% 
  #count all incorrect main trials per subject
  count(failed = correctness == "Incorrect") %>%  
  #take all subject with 50% wrong trials 
  subset(failed == "TRUE" & n >=10)

#there are no participants that got 50% of the answers wrong
xdata_wrong

##4. Exclude all data from participants who complete the experiment in under 500 ms or take longer than 6000 ms
##5.The final analysis will only concern itself with correct trial

xdata_capital <- xdata_main %>% 
  #only taking correct trials into account
  filter(correctness == "Correct") %>%  
  # taking out subjects who are faster than 500 ms and slower than 1 min
  subset(RT >= 500 & RT <= 60000 & submission_id != "2129") %>% 
  #taking out for analysis non-relevant variables
  select(-c(QUD, age, comments, education, MI, gender, languages, experiment_id,option1, option2, response,
            trial_name, trial_number, hand_question, mouse_question))

xdata_capital

```

- No subjects had all training trials wrong
- Subject 2129 had 10 incorrect answers - taking out subject 2129

##MOUSETRAP

#TRAJECTORY PREPROCESSING

```{r}
#tibble into data frame for mousetrap object
head(as.data.frame(xdata_capital))



#creating mousetrap object for further anaylsis 
mt_data_capital <- mt_import_mousetrap(xdata_capital)

#all trajectories are remapped to the left 
mt_data_capital <- mt_remap_symmetric(mt_data_capital)

#setting the starting point of the trajectories equally 
mt_data_capital <- mt_align_start(mt_data_capital, start=c(0,0))

mt_data_capital <- mt_derivatives(mt_data_capital)
#important for later creating MAD and AUC values 
mt_data_capital <- mt_measures(mt_data_capital)

#time-normalizing trajectories 
mt_data_capital <- mt_time_normalize(mt_data_capital)


#plot aggregated time-normalized trajectories 
mt_plot_aggregate(mt_data_capital, use="tn_trajectories", x="xpos", y="ypos", color="typicality",
subject_id="submission_id")+
    ggtitle("Fig. 1")

```

Fig. 1: Display of over all trials avaraged trajactory for each trial type. All trajectories have been flipped to the left. Starting and end point was set equall over all trajectories of each trail type. 

#AGGREGATE TRAJECTORY CURVATURE

```{r}

#aggregating maximum absolut deviation (MAD) values for analysis
agg_mad_capital <- mt_aggregate_per_subject(mt_data_capital,
use_variables="MAD", use2_variables="typicality",
subject_id="submission_id")

agg_auc_capital <- mt_aggregate_per_subject(mt_data_capital,
use_variables="AUC", use2_variables="typicality",
subject_id="submission_id")

```

#CLUSTER AGGREGATION & PROTOTYPE CLASSIFICATION

```{r}

#Spatialize trajectories 
mt_data_capital <- mt_spatialize(mt_data_capital)

#Cluster trajectories 
mt_data_capital <- mt_cluster(mt_data_capital, use = "sp_trajectories")

mt_plot(mt_prototypes,facet_col="mt_id",only_ggplot = TRUE)+
  geom_path()+
  facet_grid(cols = vars(factor(mt_id,levels=rownames(mt_prototypes))))+
  theme(axis.text=ggplot2::element_blank(),axis.ticks=ggplot2::element_blank()) 

mt_data_capital <- mt_map(mt_data_capital,prototypes = mt_prototypes,
  save_as = "measures", grouping_variables = "typicality")
mt_data_capital$data$prototype_label <- mt_data_capital$measures$prototype_label

prototype_percentages <- mt_data_capital$data %>%
  group_by(typicality,prototype_label) %>%
  summarise(n=n()) %>%
  mutate(Percent=paste(round(100*n/sum(n)),"%",sep=""))

mt_plot(mt_data_capital, use = "sp_trajectories",
  x = "xpos", y = "ypos", facet_col = "prototype_label", facet_row="typicality",alpha=.2)+
  xlab("x coordinate (px)") + ylab("y coordinate (px)")+
  geom_text(data=prototype_percentages,aes(label=Percent),x=650,y=50)+
  scale_y_continuous(breaks=c(0,500,1000))+
  coord_cartesian(xlim=c(-900,900))+
    ggtitle("Fig. 1")
```



Fig. 1: The plot shows the percentages of trajectories for each trial type, which are assigned to the respective trajectory prototypes. 


```{r}

rel_freq_agg <- mt_data_capital$data %>%
  group_by(typicality,prototype_label) %>%
  summarise(n=n()) %>%
  mutate(Percent=n/sum(n))

ggplot(rel_freq_agg,aes(x=typicality,y=Percent,fill=forcats::fct_rev(prototype_label)))+
  geom_bar(stat="identity",color="black")+
  scale_fill_brewer(type="seq",name="Classification")+
  facet_grid()+
    ggtitle("Fig. 2")

```


Fig.2: The graph illustrates the proportion of trajectory prototypes for each trial type. The proportion is given in percent. 

#Bimodality check

```{r}

# Standardize AUC per participant
mt_data_capital <- mt_standardize(mt_data_capital, use_variables = "AUC", within = "submission_id")

# Calculate bimodality coefficient
 mt_check_bimodality(mt_data_capital, use_variables = "z_AUC",
   grouping_variables = "typicality", methods = "BC")


# Standardize MAD per participant
mt_data_capital <- mt_standardize(mt_data_capital, use_variables = "MAD", within = "submission_id")

# Calculate bimodality coefficient
 mt_check_bimodality(mt_data_capital, use_variables = "z_MAD",
   grouping_variables = "typicality", methods = "BC")

# Standardize MAD per participant
mt_data_capital <- mt_standardize(mt_data_capital, use_variables = "RT", within = "submission_id")

# Calculate bimodality coefficient
 mt_check_bimodality(mt_data_capital, use_variables = "z_RT",
   grouping_variables = "typicality", methods = "BC")  
 
 # Standardize MAD per participant
mt_data_capital <- mt_standardize(mt_data_capital, use_variables = "initiation_time", within = "submission_id")

# Calculate bimodality coefficient
 mt_check_bimodality(mt_data_capital, use_variables = "z_initiation_time",
   grouping_variables = "typicality", methods = "BC")

```

```{r}
 
#plot trajectories 
mt_heatmap_ggplot(mt_data_capital)


#plot clustered trajectories 
mt_plot(mt_data_capital,use="sp_trajectories",
  use2="clustering",facet_col="cluster")+
    ggtitle("Fig. 3")


```



Fig.3: The graph displays the given trajectories from the data for each cluster type.


```{r}
#store mousetrap object in results
results <- merge(mt_data_capital$data, mt_data_capital$measures, by="mt_id")

#export results in long format for further analysis 
agg_xdata_capital <- mt_export_long(results)

#as tibble for easier handling
head(as.tibble(agg_xdata_capital))

##6. Trials which contain more than three flips along the y-axis will be taken out from the analysis

#creating final data table for bayesian inference 
capital <- agg_xdata_capital %>% 
    select(-c(endTime, mousetrackingStartTime, startDate, startTime, startingTime, timeSpent, xpos_max, xpos_min, xpos_reversals, ypos_max, ypos_min, MAD_time,MD_above, MD_above_time, RT.y, idle_time, vel_max, vel_max_time, vel_min, vel_min_time, acc_max, acc_max_time, min_dist, prototype, z_MAD, MD_below, MD_below_time, AD, ypos_reversals, acc_min, acc_min_time, originX, originY, prototype_label.x, correct)) %>% 
  #taking out all trials which have 3 or more flips along the x and y-axis
  subset(xpos_flips <= 3 & ypos_flips <= 3) %>% 
  rename(RT = RT.x, unique_trial_id = mt_id, trial_type = typicality, prototype_label = prototype_label.y, subject_id = submission_id,
         exemplar = question) 


capital

write.csv(capital, "~/CS-SS20/Experimental_Psychology_Lab/Final_Project/XPLab2020_FinalProject/main/Capital Study/capital_data.csv", row.names = FALSE)

```